Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-28 paper/paper.tex
More words

?? Search

we introduce a symmetry
break (line~\ref{line:sym}) to try only a single wildcard value for each variable.

?? Heuristics

Wildcards are treated as having degree zero, in an attempt to maximising the expected number of
solutions remaining during search \citep{DBLP:conf/ijcai/McCreeshPT16}. This technique allows us to
retain the bit-parallel all different propagator used in the original algorithm.

>>>>

?? This technique allows us to retain the bit-parallel all different propagator used in the original
algorithm.

If propagation is unable to prove unsatisfiability, we search. We pick the smallest domain (line
??), and try giving it each of its remaining values in turn. We use the value the ordering heuristic
from the original algorithm; wildcards are treated as having degree zero, in an attempt to
maximising the expected number of solutions remaining during search
\citep{DBLP:conf/ijcai/McCreeshPT16}.  We introduce a symmetry break (line~\ref{line:sym}) to try
only a single wildcard value for each variable.
